Draft_Mid_Term

### 2022-10-06 Draft_Mid_Term.Rmd
10/6 Update
feature selection added

```{r}
ggplot()+
  geom_sf(data=st_union(zipcode))+
  geom_sf(data=park_amenities.sf)
```
```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=park_easement.sf)
```

@@

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables\n(internal features)\n")+plotTheme()
```
remove AGE, units is a good feature do not have strong correlation with other features and have strong corelation with price.
```{r}
sel.internal.list <-  c("price",
                "shape_Area",
                "pricepersq",
                "heatedarea",
                "numfirepla",
                "fullbaths",
                "halfbaths",
                "bedrooms",
                "units")
```

@@

#stargazer:
stargazer(amenities_feature.list, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```
```{r amenities_feature_matrix}
ggcorrplot(
  round(cor(amenities_feature.list), 1), 
  p.mat = cor_pmat(amenities_feature.list),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
  labs(title = "Correlation across numeric variables\n(amenity features)\n")+plotTheme()+
  theme(axis.title.x = element_text(size=3),axis.title.y = element_text(size=3))
```

```{r}
sel.amenitie<-model_set%>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()
```

```{r}
tract.list <- c("pctTotalVacant", "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery", "test.elementary","test.middle", "test.high","PctBachelor","MedAge",'price')

@@

sel.tract.list<- c( "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery",  "test.high","PctBachelor","MedAge",'price')
```
## 2.3 Regression for Feature Selection
### 2.3.1 non numeric Feature Selection

@@

```{r}
names(nonnumeric)
```
```{r}
a = ls()
rm(list=a[which(a!='data' & a !='sel.internal.list' & a !='sel.tract.list' & a !='sel.amenitie' & a!='challenge_set'& a!= 'model_set')])
```

```{r}

nonnumeric.feature1 <- c("descbuildi", "storyheigh", "aheatingty", "heatedfuel", "extwall", "foundation", "bldggrade","price")

nonnumeric <- model_set %>% dplyr::select(nonnumeric.feature1)%>% 
  st_drop_geometry()

```
"stname", "sttype",  "city", "state",

```{r}
M1 <- lm(price ~ ., data = nonnumeric)
```

```{r}
summary(M1)
```

```{r}
sel.internal<-model_set %>% dplyr::select(sel.internal.list) %>% st_drop_geometry()

M2 <- lm(price ~ ., data = sel.internal)
```
```{r}
summary(M2)
```

```{r}
sel.tract<-model_set %>% dplyr::select(sel.tract.list) %>% st_drop_geometry()
M3 <- lm(price ~ ., data = sel.tract)

@@

```{r}
M4 <- lm(price ~., data = sel.amenitie)

@@

>>>>

```{r}
ggplot()+
  geom_sf(data=st_union(zipcode))+
  geom_sf(data=business_invest)
```

```{r}
business_invest_union<-business_invest %>% st_union() %>% st_sf()

isin<-st_within(data,business_invest_union) %>% lengths>0

isin<-data.frame(isin)

data<-cbind(data,isin)
```

```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=park_easement.sf)
```

@@

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables\n(internal features)\n")+plotTheme()
```
remove AGE, units is a good feature do not have strong correlation with other features and have strong corelation with price.
```{r}
sel.internal.list <-  c("price",
                "shape_Area",
                "heatedarea",
                "numfirepla",
                "fullbaths",
                "halfbaths",
                "bedrooms",
                "units")
```

@@

#stargazer:
stargazer(amenities_feature.list, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```

```{r amenities_feature_matrix}
ggcorrplot(
  round(cor(amenities_feature.list), 1), 
  p.mat = cor_pmat(amenities_feature.list),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
  labs(title = "Correlation across numeric variables\n(amenity features)\n")+plotTheme()+
  theme(axis.title.x = element_text(size=3),axis.title.y = element_text(size=3))
```

```{r}
#Amenities
sel.amenitie<-model_set%>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()
```

```{r}
#Tract Feature
tract.list <- c("pctTotalVacant", "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery", "test.elementary","test.middle", "test.high","PctBachelor","MedAge",'price')

@@

sel.tract.list<- c( "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery",  "test.elementary","PctBachelor","MedAge",'price')
```

```{r histogram_train_feature}
model_set %>% 
  st_drop_geometry() %>% 
  dplyr::select(price,extwall,storyheigh,heatedfuel,aheatingty,bldggrade) %>%
   filter(price <= 5000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_bar(position = "dodge", stat = "summary", fun = mean) +
     facet_wrap(~Variable, ncol = 3, scales = "free") +
     labs(title = "Price as a function of\ncategorical variables", y = "Mean_Price") +
     theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r feature_enginneering_nonnumeric}
# 1.Modify extwall:
extwall.stone<-c("STONE")
data <- 
  data %>%
  mutate(extwall.m = ifelse(extwall %in% extwall.stone,"STONE","Non-STONE"))

# 2.Modify Aheatingty:
hotwater<-c("HOT WATER")
data<-data %>% mutate(aheatingty.m = ifelse(aheatingty %in% hotwater,"HOT WATER","ELSE" ))

# 3.Modify heatedfuel:
gas<-c("GAS")
data<-data %>% mutate(heatedfuel.m = ifelse(heatedfuel %in% gas,"GAS","ELSE" ))

# 4.Modify bldggrade
fairplus<-c("FAIR","MINIMUM","NA")
data<-data %>% mutate(bldggrade.m = ifelse(bldggrade %in% fairplus,"ELSE",bldggrade))

# 5.Modify storyheigh
storyelse<-c("NA","SPLIT LEVEL","BI-LEVEL","CAPE COD","RANCH W/BSMT")
data<-data %>% mutate(storyheigh.m = ifelse(storyheigh %in% storyelse,"ELSE",storyheigh ))
```

## 2.3 Regression for Feature Selection
### 2.3.1 non numeric Feature Selection

```{r}
outlier<-data %>% filter(price>2200000)
```

```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=outlier)
```

```{r challenge_set}
#challenge_set:用于最后预测的组，crs=4326
challenge_set<-data %>% filter(price==0)
```

```{r model_set}
#model_set:建模组,crs=4326
model_set<-data %>% filter(price!=0)
```

@@

```{r}
names(nonnumeric)
```

```{r,eval=FALSE}
#删除不再使用的数据集合
#a = ls()
#rm(list=a[which(a!='data' & a !='sel.internal.list' & a !='sel.tract.list' & a !='sel.amenitie' & a!='challenge_set'& a!= 'model_set')])
```

```{r}
#非数字的列
nonnumeric.feature1 <- c("descbuildi", "storyheigh.m", "aheatingty.m", "heatedfuel.m", "extwall.m", "foundation", "bldggrade.m","isin","price")
```
"stname", "sttype",  "city", "state",

## 4.1 Dataset Splitting and Model Building

```{r model_set_split,warning=FALSE}
#1.Split Model Set:
set.seed(7278)

# get index for training sample:
inTrain<-caret::createDataPartition(
  y = paste(model_set$storyheigh,model_set$extwall,model_set$bldggrade,model_set$price),
  p = .60, 
  list=FALSE)

# split model_set into train and test
model_set.train<-model_set[inTrain,] %>% filter(price<=2200000)
model_set.test<-model_set[-inTrain,]
```

```{r}
#non-numeric feature
nonnumeric <- model_set.train %>% dplyr::select(nonnumeric.feature1)%>% 
  st_drop_geometry()
```

```{r M1_nonnumeric}
#第一个lm:回归非数字类型的列
M1 <- lm(price ~ ., data = nonnumeric)

summary(M1)
```

```{r M2_internal_feature}
# internal feature
sel.internal<-model_set.train %>% dplyr::select(sel.internal.list) %>% st_drop_geometry()
M2 <- lm(price ~ ., data = sel.internal)

summary(M2)
```

```{r M3_tract_feature}
sel.tract<-model_set.train %>% dplyr::select(sel.tract.list) %>% st_drop_geometry()
M3 <- lm(price ~ ., data = sel.tract)

@@

```{r }
sel.amenitie1<-model_set.train%>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()

M4 <- lm(price ~., data = sel.amenitie1)

@@

```{r}
train_set.1<-model_set.train %>% dplyr::select(
  price,
  #Non-numeric Feature
  descbuildi,bldggrade,
  #Internal Feature
  shape_Area , heatedarea , numfirepla , halfbaths , fullbaths , bedrooms , units,
  #Tract Feature
  pctRenterOccupied , pctWhite , pctPoverty , MedRent , MedHHInc , PctLongCommute, Pctgrocery, PctBachelor, test.high,
  #Amenities Feature
  college_nn2, daycare_nn5,MedicalFacilities_nn5,library_nn5,hist_cemeteries_nn1,hist_properties_nn4, hist_properties_nn5,capital_improve_nn2,capital_improve_nn3,capital_improve_nn4,capital_improve_nn5) %>% st_drop_geometry()

M5 <- lm(price ~ ., data = train_set.1)

summary(M5)
```

```{r backup}
train_set.2<-model_set.train %>% dplyr::select(
  price,
  #Non-numeric Feature
  bldggrade.m,storyheigh.m,foundation,
  #Internal Feature
  shape_Area ,heatedarea, numfirepla,fullbaths,halfbaths, bedrooms , units,
  #Tract Feature
  pctRenterOccupied , pctWhite ,pctPoverty,MedHHInc ,test.elementary,PctBachelor,crime_sum,PctLongCommute,Pctgrocery,
  #Amenities Feature
  college_nn5,daycare_nn1,MedicalFacilities_nn4,MedicalFacilities_nn5,library_nn3,library_nn4,library_nn2,hist_properties_nn5,capital_improve_nn3,capital_improve_nn4,capital_improve_nn5) %>% st_drop_geometry()

M6 <- lm(price ~ ., data = train_set.2)

summary(M6)
```

```{r all_features}
train_set.lipu<-model_set.train %>% dplyr::select(price,
  nonnumeric.feature1,sel.internal.list,sel.tract.list,
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_')
) %>% st_drop_geometry()

M_0 <- lm(price ~ ., data = train_set.lipu)

summary(M_0)
```
